---
title: "Developing Data Product Assignment Week 3"
author: "Bert Haak"
date: "March 25, 2017"
output:
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment 

This presentation contains a graph made with plotly of the dataset Wage from the ISLR library.
The following steps were taken:

1. Made a plot of the data with ggplot2.
2. Used the ggplotly function from plotly to transform the ggplot to plotly
3. For practice changed the following plotly parameters directly:

        a. Added a Title to the plot
        b. changed the Legend of the plot
        c. Changed the hover text

***

```{r, message=FALSE, cache=TRUE, warning=FALSE, fig.height=5.5 ,fig.width = 8.5}
library(ggplot2); library(plotly); library(ISLR)
data(Wage)
g <- ggplot(data = Wage, aes(x = age, y = wage))
g <- g + geom_point(size = 2, pch = 21, aes(fill = factor(education)), alpha = 1)
g <- g + xlab("Age of Worker") + ylab("Workers' raw wage")
g <- g + labs(fill = "Education")
g <- g + geom_smooth(formula = y ~ x, method = "lm", aes(colour = factor(education)), show.legend = FALSE)
p <- ggplotly(g)
p$x$data[[1]]$name <- "< HS Grad"
p$x$data[[2]]$name <- "HS Grad"
p$x$data[[3]]$name <- "College"
p$x$data[[4]]$name <- "College Grad"
p$x$data[[5]]$name <- "Advanced Degree"
p$x$layout$title <- "Mid-Atlantic Wage Data"
for(i in 1:5){
        p$x$data[[i]]$text <- gsub("factor\\(education\\)", "Education", p$x$data[[i]]$text)
        if(i == 1){p$x$data[[i]]$text <- gsub("1. < HS Grad", "< HS Grad", p$x$data[[i]]$text)}
        if(i == 2){p$x$data[[i]]$text <- gsub("2. HS Grad", "HS Grad", p$x$data[[i]]$text)}
        if(i == 3){p$x$data[[i]]$text <- gsub("3. Some College", "College", p$x$data[[i]]$text)}
        if(i == 4){p$x$data[[i]]$text <- gsub("4. College Grad", "College Grad", p$x$data[[i]]$text)}
        if(i == 5){p$x$data[[i]]$text <- gsub("5. Advanced Degree", "Advanced Degree", p$x$data[[i]]$text)}
}
p
```
